Scalable machine learning pipelines for waterbody delineation, classification, and change detection

### 2023-07-17 manuscript/manuscript.tex
manuscript templating

\author{ \href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Jemma Stachelek} \\
	Earth System Observations\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
}

@@

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.000/XXXXX}}
\renewcommand{\undertitle}{This is an Accepted Manuscript of an article published in Journal \href{https://doi.org/10.1000/XXXXX}{DOI: 10.1000/XXXXX}}
\renewcommand{\shorttitle}{ML pipelines for waterbody imagery}

@@

\begin{figure}
	\centering
	\includegraphics{figures/single_wb}
	\caption{This is a caption}
	\label{fig:predict_censor}
\end{figure}

>>>>

\author{ \href{https://orcid.org/0000-0002-5924-2464}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Jemma Stachelek}, Charles J. Abolt, Jon Schwenk \\
	Earth and Environmental Sciences\\
	Los Alamos National Laboratory\\
	Los Alamos, NM, USA, 87544 \\
	\texttt{jsta@lanl.gov} \\
}

@@

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.000/XXXXX}}
\renewcommand{\undertitle}{This is a draft of a Manuscript in preparation for publication in Geophysical Research Letters \href{https://doi.org/10.1000/XXXXX}{DOI: 10.1000/XXXXX}}
\renewcommand{\shorttitle}{ML pipelines for waterbody imagery}

@@

\begin{figure}
	\centering
	\includegraphics{../figures/single_wb}
	\caption{This is a caption}
	\label{fig:single_wb}
\end{figure}
